Can Zero-shot Large Language Models save additional work in machine learning prioritised screening for systematic reviews?

### 2024-11-08 LLMs/manuscript/main.tex
Updates from Overleaf

\title{Can Zero-shot LLMs save additional work in machine learning prioritised screening for systematic reviews?}
\author[1,2]{Max Callaghan}

@@

	\begin{abstract}
		Zero shot learning using LLMs has received widespread attention in recent years, including in the automation of systematic review screening. 
		However, there has been insufficient research on robust processes to automate screening responsibly. 
		For systematic review screening, responsible automation requires that the risks of missing relevant studies (which are inherent when the process is automated) can be accurately quantified and managed. 
		In this paper, we adapt LLM-assisted screening to the widespread machine learning prioritised screening paradigm, and use a robust stopping criterion to quantify how much work can be responsibly saved with different levels of risk tolerance for missing studies.
		We find that - even in the absence of detailed inclusion and exclusion criteria - LLM-assisted screening can produce ranked lists of documents that are superior to those generated by our baseline - a standard active learning approach using a support vector machine.
		However, LLMs do not seem to be a silver bullet which would substantially reduce the amount of work required to complete screening. Across a variety of recall targets and confidence levels, work savings were generally higher with the SVM baseline, though possible work savings with LLMs were higher in low recall or low confidence settings. 
	\end{abstract}

@@

	We now turn to the work savings that would have been achieved at the stopping points given by the stopping criteria. Table \ref{tab:wssp} shows the mean and standard deviation of the work savings achieved for each combination of model, recall target, and confidence level. For low recall targets and low levels of confidence, large work savings are possible (>50\%). Increasing either the recall target or the level of confidence reduces the work savings that can be achieved. For example, for a recall target of 99\%, it is still possible to achieve work savings of 28.8\%, as long as one accepts a 50-50 chance of missing the target. However, if one wants to be 99\% confident that a 99\% recall target has not been missed, on average one would only save 1.6\% of the work.

@@

@@

>>>>

\title{Can Zero-shot Large Language Models save additional work in machine learning prioritised screening for systematic reviews?}
\author[1,2]{Max Callaghan}
\author[1,2]{Jan Minx}

@@

	\begin{abstract}
		Zero shot learning using Large Language Models (LLMs) has received widespread attention in recent years, including in the automation of systematic review screening. 
		However, there has been insufficient research on robust processes to automate screening responsibly. 
		For systematic review screening, responsible automation requires that the risks of missing relevant studies (which are inherent when the process is automated) can be accurately quantified and managed. 
		In this paper, we adapt LLM-assisted screening to the widespread machine learning prioritised screening paradigm, and use a robust stopping criterion to quantify how much work can be responsibly saved with different levels of risk tolerance for missing studies.
		We find that - even in the absence of detailed inclusion and exclusion criteria - LLM-assisted screening can produce ranked lists of documents that are superior to those generated by our baseline - a standard active learning approach using a support vector machine.
		However, LLMs do not seem to be a silver bullet which would substantially reduce the amount of work required to complete screening. Across a variety of recall targets and confidence levels, work savings were generally higher with the SVM baseline, though possible work savings with LLMs were higher in low recall or low confidence settings. 
	\end{abstract}

@@

	We now turn to the work savings that would have been achieved at the stopping points given by the stopping criteria. Table \ref{tab:wssp} shows the mean and standard deviation of the work savings achieved for each combination of model, recall target, and confidence level. For low recall targets and low levels of confidence, large work savings are possible (\textgreater50\%). Increasing either the recall target or the level of confidence reduces the work savings that can be achieved. For example, for a recall target of 99\%, it is still possible to achieve work savings of 28.8\%, as long as one accepts a 50-50 chance of missing the target. However, if one wants to be 99\% confident that a 99\% recall target has not been missed, on average one would only save 1.6\% of the work.

@@

    \section*{Code Availability}

    The code required to reproduce the results of this study is made availabel at \url{https://github.com/mcallaghan/ml-screening-evaluation}

@@

        \subsubsection*{Llama3.1}

        \begin{verbatim}
    <|begin_of_text|><|start_header_id|>system<|end_header_id|>
    You are a systematic review helper tasked with finding out whether a study is relevant to the review $t

    Answer 'yes' if the study is relevant, or 'no' if not
    <|eot_id|><|start_header_id|>user<|end_header_id|>

    Study: $s

    Should the study be included? Answer yes or no. <|eot_id|>

    <|start_header_id|>assistant<|end_header_id|>

        \end{verbatim}

        \subsubsection*{Llama2}
        \begin{verbatim}
    <s>[INST] <<SYS>>
    You are a systematic review helper tasked with finding out 
    whether a study is relevant to the review $t

    Answer 'yes' if the study is relevant, or 'no' if not
    <</SYS>>

    Study: $s

    Should the study be included? Answer yes or no. [/INST] 
        \end{verbatim}
